Discovering causal factors with back-to-back regression

### 2019-05-22 paper/meg_exps.tex
wip: meg

For each word, each subject, and each time sample relative to word onset, we build an observation matrix $Y \in \mathbb{R}^{n, q}$ of $n\approx$ 2700 words by $q=301$ MEG channels (273 magnetometers and 28 compensation channels). Each of the columns of $Y$ is normalized to have a mean and a standard deviation of 0 and 1 respectively.

@@

\subsection{Analyses}
We aim to identify which factors of $X$ explain the MEG recordings $Y$ at each time sample and for each subject separately. To this aim, we implemented three types of analyses (forward, backward and back-to-back regressions), and tested whether their results were consistent across subjects, using a second-level statistics described below.

Forward regression, also known as 'encoding' in neuroimaging, here consisted in fitting a Ridge-regularized OLS from $X$ to $Y$:
\begin{equation}
H = (X^{T}X+\lambda I)^{-1} X^{T}Y
\end{equation}
where $\lambda$ is the regularization parameter fit with the leave-one-out cross-validation implemented in scikit-learn \cite{sklearn} from 20 possible value logarithmatically distributed between $10^{-5}$ and $10^5$. We aim to estimate the contribution $diag(\hat E) \in\mathbb{D}^{d} $ of each factor. However, $H\in\mathbb{R}^{d, q}$ is a matrix of $d$ word features by $q$ MEG channels. We thus approximate the relative contribution of each feature by sum-squarring the H coefficients:
\begin{equation}
\hat e_d = \sum_{i=0}^{i=q} {h_d^i}^2
\end{equation}

Backward regression, also known as 'decoding' in neuroimaging, here consisted in fitting a Ridge-regularized OLS from $Y$ to $X$:
\begin{equation}
G = (Y^{T}Y+\lambda I)^{-1} Y^{T}X
\end{equation}
where $\lambda$ is the regularization parameter fit with the leave-one-out cross-validation implemented in scikit-learn \cite{sklearn} from 20 possible value logarithmically distributed between $10^{-5}$ and $10^5$. We aim to estimate the contribution $diag(\hat E) \in\mathbb{D}^{d} $ of each factor. Using 10-fold cross-validation, we thus assessed the ability of this ridge regression to predict independent and identically distributed data:
\begin{equation}
\hat X_{test} = Y_{test}\cdot G_{train}
\end{equation}
and assessing, for each factor of X independently, the Pearson correlation coefficient $r$ between $X_{test}$ and $\hat X_{test}$ for each cross-validation split.

Models were fit for each subject and for each time sample independently

Using this dataset, we study which word features cause a brain response detectable
via MEG.

 $\left(n \times 38\right)$-dimensional input matrix $X$,
where $n$ is the number of words for the subject. Each feature in $X$ is centered and
scaled for zero mean and unit variance.

Then, we apply the BFR method independently on each of the 67 time slices of the
MEG recordings. Each slice $Y_t$ is a $n \times 301$ matrix, also centered and
scaled. We obtain a vector of 38 coefficients per slice.

>>>>

For each word, each subject, and each time sample relative to word onset, we build an observation matrix $Y \in \mathbb{R}^{n, q}$ of $n\approx$ 2700 words by $q=301$ MEG channels (273 magnetometers and 28 compensation channels). Each of the columns of $Y$ is normalized to have zero mean and unit variance.

@@

\subsection{Analyses}
We aimed to identify which factors of $X$ explain the MEG recordings $Y$ at each time sample and for each subject separately. To this aim, we implemented three types of analyses (forward, backward and back-to-back regressions), and tested whether their results were consistent across subjects, using a second-level statistics described below.

Forward regression, also known as 'encoding' in neuroimaging, here consisted in fitting a Ridge-regularized OLS from $X$ to $Y$:
\begin{equation}
H = (X^{T}X+\lambda I)^{-1} X^{T}Y
\end{equation}
where $\lambda$ is the regularization parameter fit with the leave-one-out cross-validation implemented in scikit-learn \cite{sklearn} from 20 possible value logarithmatically distributed between $10^{-5}$ and $10^5$. We aimed to estimate the contribution $diag(\hat E) \in\mathbb{D}^{d} $ of each factor. However, $H\in\mathbb{R}^{d, q}$ is a matrix of $d$ word features by $q$ MEG channels. We thus approximated the relative contribution of each feature by sum-squarring the H coefficients:
\begin{equation}
\hat e_d = \sum_{i=0}^{i=q} {h_d^i}^2
\end{equation}

Backward regression, also known as 'decoding' in neuroimaging, here consisted in fitting a Ridge-regularized OLS from $Y$ to $X$:

\begin{equation}
G = (Y^{T}Y+\lambda I)^{-1} Y^{T}X
\end{equation}

where $\lambda$ is the regularization parameter fit with the leave-one-out cross-validation
implemented in scikit-learn \cite{sklearn} from 20 possible value logarithmically distributed
between $10^{-5}$ and $10^5$. We aimed to estimate the contribution $diag(\hat E)
\in\mathbb{D}^{d} $ of each factor. Using 10-fold cross-validation, we thus assessed the ability
of this ridge regression to predict independent and identically distributed data:

\begin{equation}
\hat X_{test} = Y_{test}\cdot G_{train}
\end{equation}

and assessing, for each factor of X independently, the Pearson correlation coefficient $r$ between $X_{test}$ and $\hat X_{test}$ for each cross-validation split.

Finally, back-to-back regression was fit as decribed earlier using two additional stability tricks designed to minimize the impact of bagging.
First the $G$ ridge regression was broken-down with SVD blablabla
Second, $X$ was regularized using a maximal likelihood blablabla
Third, no regularization

Back-to-back regression directly leads to $\hat E$.

\subsection{Second-level statistics}

The three types of analyses were implemented for each subject and each time sample independently.
To estimate the reliability of these estimates in the population, we tested, using one-sample t-test whether the distribution of the estimated contribution of each factor different from baseline ($t=-100$ms):

\begin{equation}
$ttest(\hat E_{t=-100} - \hat E_{\tau}$
\end{equation}
with $\tau \in $ 150ms and 400ms respectively

\subsection{Results}

We aimed to estimate
